
\documentclass[conference]{IEEEtran}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{algpseudocode}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{subcaption}
%code block
\usepackage{listings}
\usepackage{xcolor}

\usepackage[colorlinks,
linkcolor=red,
anchorcolor=black,
citecolor=black
]{hyperref}
\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\jin}[1]{\textcolor{blue}{{\it [jin add: #1]}}}



\begin{document}

\lstset{
	tabsize = 2,
	frame=single, %把代码用带有阴影的框圈起来
	commentstyle=\color{red!50!green!50!blue!50},%浅灰色的注释
	rulesepcolor=\color{red!20!green!20!blue!20},%代码块边框为淡青色
	keywordstyle=\color{blue!90}\bfseries, %代码关键字的颜色为蓝色，粗体
	showstringspaces=false,%不显示代码字符串中间的空格标记
	stringstyle=\ttfamily, % 代码字符串的特殊格式
	keepspaces=true, %
	breakindent=10pt, %
	numbers=left,%左侧显示行号
	stepnumber=1,%
	%backgroundcolor=\color{gray},
	numberstyle=\tiny, %行号字体用小号
	basicstyle=\scriptsize,
	%basicstyle=\footnotesize, %
	showspaces=false, %
	flexiblecolumns=true, %
	breaklines=true, %对过长的代码自动换行
	breakautoindent=true,%
	breakindent=2em, %
	escapebegin=\begin{CJK*}{GBK}{hei},escapeend=\end{CJK*},
	aboveskip=1em, %代码块边框
	%% added by http://bbs.ctex.org/viewthread.php?tid=53451
	fontadjust,
	captionpos=t,
	framextopmargin=2pt,framexbottommargin=2pt,abovecaptionskip=-3pt,belowcaptionskip=3pt,
	xleftmargin=2em,xrightmargin=2em, % 设定listing左右的空白
	texcl=true,
	% 设定中文冲突，断行，列模式，数学环境输入，listing数字的样式
	extendedchars=false,columns=flexible,mathescape=true
	%numbersep=0pt
}	

\pagestyle{plain}	
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Empirical Study of Just-in-Time Prediction of Performance Regression Introducing Change}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{Kundi Yao, Jinfu Chen}
\IEEEauthorblockA{Department of Software Engineering \\
Concordia University\\
Montreal, Canada\\
\{ku\_yao,fu\_chen\}@encs.concordia.ca}
}
% make the title area
\maketitle
\begin{comment}


\begin{abstract}
Performance is an important aspect of software quality. Performance issues may compromise user experiences, increase the operating cost of the system, and cause field failures. In fact, large software systems failures are often due to performance issues rather than functional bugs. One of the most prevalent performance issues is performance regression. Examples of performance regressions are response time degradation and higher than before resource utilization. Although prior research proposes various automated approaches that detect performance regressions, the detection is conducted after fact, i.e., after the system is built and deployed in the field or dedicated performance testing environments. On the other hand, there exists rich software quality research that examines the impact of code changes on software quality; while majority of prior findings do not use performance regression as a sign of software quality degradation. In this paper, we perform an exploratory study on the source code changes that introduce performance regressions. We conduct a statistically rigorous performance evaluation on 376 commits from two releases of \emph{Hadoop} and 135 commits from five releases of \emph{RxJava}. In particular, we identify performance regressions in each commit if there exists statistically significant and non-trivial performance degradation, in terms of either response time, CPU usage, Memory usage or I/O traffic, compared to the last commit. By manually examining the JIRA issue reports that are associated with the identified performance regression introducing commits, we find that the majority of the performance regressions are introduced while fixing other bugs. In addition, we find that most of such regressions are due to expensive function calls. Our findings suggest that developers may introduce performance regressions when completing code changing tasks without considering the impact on performance. Automated tooling support can be proposed to help developers be aware of the possible performance impact while changing source code.

\end{abstract}

\begin{IEEEkeywords}
Performance Regression; Code Changes; Mining Software Repositories
\end{IEEEkeywords}

\end{comment}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
\label{sec:intro}
\input{intro}

\section{Related Work}
\label{sec:related}
\input{related}

\section{Approach}
\label{sec:case}
\input{case}

\section{Case Study}
\label{sec:results}

Our study aims to answer three research questions. For each research question, we present 
the motivation for the question, the approach that we use to answer the question.

\subsection*{RQ1: How well can we predict the existence of performance regression introducing change?}
\input{rq1}

\subsection*{RQ2: How well can we predict the magnitude of performance regression introducing change?}
\input{rq2}

\subsection*{RQ3: What are the important measures of performance regression introducing change?}
\input{rq3}


%\section{Implications of Our Findings}
%\label{sec:imp}
%\input{imp}

\section{Threat to Validity}
\label{sec:threats}
\input{threats}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

\bibliographystyle{IEEEtran}
\bibliography{bibliography} 


% that's all folks
\end{document}


